True versus apparent shapes of astrophysical bow shocks

### 2017-08-08 papers/Paper1/sec-quadrics-observations.tex
Finally get back into writing. Describe fits to Herschel arcs

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.48\linewidth}
  \includegraphics[trim=10 0 60 30, clip]{figs/alphaori-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/mucep-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/rhya-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/rleo-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/uuaur-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/v1943sgr-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/xpav-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/rcas-imageplot}
  \caption{RSG and AGB shells observed with Herschel.  Selected
    Class~I sources (``fermata-like'') from the MESS survey
    \citet{Cox:2012a}, where the arc structure is particularly clear
    and symmetrical.  Left panels show PACS \SI{70}{\um} surface
    brightness (blue) and \SI{160}{\um} (orange).  Right panels show
    tracing of the bow shock arc (red symbols) and circle fit (magenta
    lines and symbols) superimposed on a low-contrast image of the
    \SI{70}{\um} surface brightness.}
  \label{fig:herschel-arc-fits}
\end{figure*}

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.48\linewidth}
  \includegraphics[trim=10 0 60 30, clip]{figs/cwleo-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/epaqr-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/khicyg-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/rtvir-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/waql-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/wpic-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/rscl-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/tetaps-imageplot}
  \caption{As Fig~\ref{fig:herschel-arc-fits}, but for a further 8
    Class~I sources from \citet{Cox:2012a} where the arc structure is
    more diffuse, weak, and/or asymmetric. For CW~Leo only (top-left),
    the right-hand panel shows a grayscale image of the \SI{160}{\um}
    rather than \SI{70}{\um} emission.}
  \label{fig:herschel-arc-fits-poor}
\end{figure*}

@@

We obtain a second sample of bow shocks from a far-infrared survey
\citep{Cox:2012a} of circumstellar shells around asymptotic giant
branch (AGB) stars and cool supergiants, obtained as part of the
\textit{Herschel} MESS (Mass-loss of Evolved StarS) program
\citep{Groenewegen:2011a}.  The survey sources were divided into four
classes by \citeauthor{Cox:2012a}, according to the overall shape of
the extended emission at \SI{70}{\um}: ``fermata~\textfermata'', or
arcs (Class~I); ``eyes~\faEye'' (Class~II); ``rings~{\Large
  \(\odot\)}'' (Class~III), and ``irregular~\staveXXV'' (Class~IV).  Of
these, only the Class~I sources clearly correspond to bow shocks,
which represent 22 out of 50 total sources detected with extended
emission.  For our sample, we select the 16 Class~I sources where the
shape parameters can be reliably measured, and which are shown in
Figures~\ref{fig:herschel-arc-fits}
and~\ref{fig:herschel-compare-mipsgal}.  In most sources, the bow
shock shell is most clearly visible in the \SI{70}{\um} band, with the
exception being CW~Leo where the \SI{180}{\um} band is used instead.

The remaining six Class~I sources (Fig.~1 of \citealp{Cox:2012a}) are
too asymmetrical or irregular to reliably determine \(R_{c}\) and
\(R_{90}\), and are therefore excluded from our sample.

>>>>

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.48\linewidth}
  \begin{tabular}{@{}ll@{}}
    (a) & (b) \\
    \includegraphics[trim=10 0 60 30, clip]{figs/alphaori-imageplot}
    & \includegraphics[trim=10 0 60 30, clip]{figs/mucep-imageplot}\\
    (c) & (d) \\
    \includegraphics[trim=10 0 60 30, clip]{figs/rhya-imageplot}
    & \includegraphics[trim=10 0 60 30, clip]{figs/rleo-imageplot}\\
    (e) & (f) \\
    \includegraphics[trim=10 0 60 30, clip]{figs/uuaur-imageplot}
    & \includegraphics[trim=10 0 60 30, clip]{figs/v1943sgr-imageplot}\\
    (g) & (h) \\
    \includegraphics[trim=10 0 60 30, clip]{figs/xpav-imageplot}
    & \includegraphics[trim=10 0 60 30, clip]{figs/rcas-imageplot}
  \end{tabular}
  \caption{RSG and AGB shells observed with Herschel.  Selected
    Class~I sources (``fermata-like'') from the MESS survey
    \citet{Cox:2012a}, where the arc structure is particularly clear
    and symmetrical.  Left panels show PACS \SI{70}{\um} surface
    brightness (blue) and \SI{160}{\um} (orange).  Right panels show
    tracing of the bow shock arc (red symbols) and circle fit (magenta
    lines and symbols) superimposed on a low-contrast image of the
    \SI{70}{\um} surface brightness. (a)~\(\alpha\)~Ori. (b)~\(\mu\)~Cep.
    (c)~R~Hya. (d)~R~Leo. (e)~UU~Aur. (f)~V1934~Sgr. (g)~X~Pav.
    (h)~R~Cas.}
  \label{fig:herschel-arc-fits}
\end{figure*}

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.48\linewidth}
  \begin{tabular}{@{}ll@{}}
    (a) & (b) \\
    \includegraphics[trim=10 0 60 30, clip]{figs/cwleo-imageplot}
    & \includegraphics[trim=10 0 60 30, clip]{figs/epaqr-imageplot} \\
    (c) & (d) \\
    \includegraphics[trim=10 0 60 30, clip]{figs/khicyg-imageplot}
    & \includegraphics[trim=10 0 60 30, clip]{figs/rtvir-imageplot} \\
    (e) & (f) \\
    \includegraphics[trim=10 0 60 30, clip]{figs/waql-imageplot}
    & \includegraphics[trim=10 0 60 30, clip]{figs/wpic-imageplot} \\
    (g) & (h) \\
    \includegraphics[trim=10 0 60 30, clip]{figs/rscl-imageplot}
    & \includegraphics[trim=10 0 60 30, clip]{figs/tetaps-imageplot}
  \end{tabular}
  \caption{As Fig~\ref{fig:herschel-arc-fits}, but for a further 8
    Class~I sources from \citet{Cox:2012a} where the arc structure is
    more diffuse, weak, and/or asymmetric. (a)~CW~Leo. For this source
    only, the right-hand panel shows a grayscale image of the
    \SI{160}{\um} rather than \SI{70}{\um}
    emission. (b)~EP~Aqr. (c)~\(\chi\)~Cyg. (d)~RT~Vir. (e)~W~Aql. (f)~W~Pic. (g)~R~Scl.
    (h)~\(\theta\)~Aps.}
  \label{fig:herschel-arc-fits-poor}
\end{figure*}

@@

We obtain a second sample of bow shocks from a far-infrared survey
\citep{Cox:2012a} of circumstellar shells around asymptotic giant
branch (AGB) stars and cool supergiants, obtained as part of the
\textit{Herschel} MESS (Mass-loss of Evolved StarS) program
\citep{Groenewegen:2011a}.  The survey sources were divided into four
classes by \citeauthor{Cox:2012a}, according to the overall shape of
the extended emission at \SI{70}{\um}: ``fermata~\textfermata'', or
arcs (Class~I); ``eyes~\faEye'' (Class~II); ``rings~{\Large
  \(\odot\)}'' (Class~III), and ``irregular~\staveXXV'' (Class~IV).  Of
these, only the Class~I sources clearly correspond to bow shocks,
which represent 22 out of 50 total sources detected with extended
emission.  For our sample, we select the 16 Class~I sources where the
shape parameters can be reliably measured, and which are shown in
Figures~\ref{fig:herschel-arc-fits}
and~\ref{fig:herschel-arc-fits-poor}. The remaining six Class~I
sources (Fig.~1 of \citealp{Cox:2012a}) are too asymmetrical or
irregular to reliably determine \(R_{c}\) and \(R_{90}\), and are
therefore excluded from our sample.

In most sources, the bow shock shell is most clearly visible in the
\SI{70}{\um} band, with the exception being CW~Leo where the
\SI{180}{\um} band is used instead.  In several sources, the shell is
split into multiple filaments, with the clearest example being
\(\alpha\)~Ori (Betelgeuse), shown in
Figure~\ref{fig:herschel-arc-fits}(a).  For such sources, we take the
outer envelope of the filaments as the bow shock arc.  Given this
complication, and the fact that the angular resolution relative to the
bow shock size is much better than in the MIPSGAL sources, we judge
that the arc tracing is best performed by eye and this is carried out
using the SAOImage~DS9 FITS viewer \citep{Joye:2003a}, with results
shown as small red open circles in Figures~\ref{fig:herschel-arc-fits}
and~\ref{fig:herschel-arc-fits-poor}.  Subsequently, the bow shock
parameters \(R_0\), \(R_{90}\), and \(R_c\) are determined by circle
fits, as in steps 5--8 of \S~\ref{sec:autom-trac-fitt}, with results
shown in magenta on the figures.
